---
title: "lobster_exploration"
format: html
editor: visual
---

```{r}
library(tidyverse)
library(here)
library(janitor)
library(lterdatasampler)
```

## Day 6 Activities

### **Find counts and mean sizes by site & year**

```{r}
lob_abundance_all_years <- read_csv(here("data","Lobster_Abundance_All_Years_20210412.csv"), na = c("-99999", "")) %>% clean_names() %>% uncount(count)
```

```{r}
# Reminder: group_by + summarize
counts_mean_by_site_year <- lob_abundance_all_years %>% 
  group_by(site,year) %>% 
  summarize(mean_size = mean(size_mm), n = n())
```

```{r}
ggplot(data = counts_mean_by_site_year, aes(x = year, y = n))+
  geom_point(aes(color = site))
```

### **Find the proportion of legal lobsters at each site for 2020**

```{r}
subset_2020 <- lob_abundance_all_years %>% 
  filter(year %in% 2020) %>% group_by(site) %>% 
  mutate(legal_limit = case_when(size_mm >= 79.76 ~ "Above", size_mm < 79.76 ~ "Below"))


limit_subset <- subset_2020 %>% 
  group_by(site,legal_limit) %>% 
  summarize(n=n())



ggplot(data = limit_subset, aes(x = site, y = n, fill = legal_limit))+
  geom_col(position = "fill")
```

### **filter() practice**

1.  Create and store a subset that only contains lobsters from sites \"IVEE\", \"CARP\" and \"NAPL\". Check your output data frame to ensure that only those three sites exist.

2.  Create a subset that only contains lobsters observed in August.

3.  Create a subset with lobsters at Arroyo Quemado (AQUE) **OR** with a carapace length greater than 70 mm.

4.  Create a subset that does NOT include observations from Naples Reef (NAPL)

```{r}
subset_by_site <- lob_abundance_all_years %>% 
  filter(site %in% c("IVEE", "CARP", "NAPL"))

subset_by_site_August <- lob_abundance_all_years %>% 
  filter(month %in% 8)

subset_AQUE_or <- lob_abundance_all_years %>% 
  filter(site %in% "AQUE" | size_mm > 70)

exclude_NAPL <- lob_abundance_all_years %>% 
  filter(site != "NAPL")
```

### **group_by() %\>% summarize() practice**

5.  Find the mean and standard deviation of lobster carapace length, grouped by site.

6.  Find the maximum carapace length by site and month.

```{r}
lob_mean_sd_by_site <- lob_abundance_all_years %>% group_by(site) %>% summarize(mean_size = mean(size_mm, na.rm = TRUE), sd_size = sd(size_mm, na.rm = TRUE))

lob_max_length_by_site_month <- lob_abundance_all_years %>% group_by(site,month) %>% summarize(max_size = max(size_mm, na.rm = TRUE))
```

### **mutate() practice**

7.  Add a new column that contains lobster carapace length converted to centimeters. Check output.

8.  Update the site column to all lowercase. Check output.

9.  Convert the area column to a character (not sure why you\'d want to do this, but try it anyway). Check output.

```{r}
lobs_cm<-lob_abundance_all_years %>% 
  mutate(length_cm = size_mm / 10)

site_lowercase <- lob_abundance_all_years %>% 
  mutate(site = tolower(site))

area_character <- lob_abundance_all_years %>% 
  mutate(area_chr = as.character(area))
```

### **case_when() practice**

10. Use `case_when()` to add a new column called `size_bin` that contains \"small\" if carapace size is \<= 70 mm, or \"large\" if it is greater than 70 mm. Check output.

11. Use `case_when()` to add a new column called `designation` that contains \"MPA\" if the site is \"IVEE\" or \"NAPL\", and \"not MPA\" for all other outcomes.

```{r}

```
